Notes on 10d Super Yang-Mills

### 2019-03-22 10d_SYM_Notes.tex
U(5)-invariant SUSY

\newcommand{\map}{\ul{\mr{Map}}}
\newcommand{\dBRST}{\mathrm d_{\mathrm{BRST}}}
\renewcommand{\d}{\mathrm{d}}
\newcommand{\sD}{\slashed{D}}
\newcommand{\sdel}{\slashed{\partial}}
\newcommand{\cO}{\mathcal{O}}
\newcommand{\sdelbar}{\overline{\slashed{\partial}}}
\newcommand{\st}[1]{{}^*{#1}}

@@

>>>>

\newcommand{\C}{\mathbf{C}}
\newcommand{\dBRST}{\mathrm d_{\mathrm{BRST}}}
\renewcommand{\d}{\mathrm{d}}
\newcommand{\sD}{\slashed{D}}
\newcommand{\sdel}{\slashed{\partial}}
\newcommand{\map}{\ul{\mr{Map}}}
\newcommand{\cO}{\mathcal{O}}
\newcommand{\sdelbar}{\overline{\slashed{\partial}}}
\newcommand{\st}[1]{{}^*{#1}}

@@

\subsection{$U(5)$-invariant splitting}

Pick a reduction of the structure group to $U(5)\subset SO(10)$. This splits the defining representation as $\C^{10} = L\oplus L^*$ giving a decomposition $A = A_{0, 1} + A_{1, 0}$. Therefore, $\wedge^2 \C^{10} \cong \wedge^2 L \oplus \End(L) \oplus \wedge^2 L^*$ which gives a decomposition $F = F_{2, 0} + F_{1, 1} + F_{0, 2}$. We denote by $J\colon \End(L)\rightarrow \C$ the trace. The semi-spin representation splits as $S_+ = (\C\oplus \wedge^2 L\oplus \wedge^4 L)\otimes \det(L)^{-1/2}$ giving a decomposition $\lambda = \chi + B + \psi$.

If $Q\in S_+$ is the scalar supercharge, the supersymmetry transformations become
\begin{align*}
\delta_Q A_{1, 0} &= Q\psi \\
\delta_Q B &= Q F_{0, 2} \\
\delta_Q \chi &= -\frac{1}{2}Q J(F_{1, 1}).
\end{align*}
Note that $\delta_Q^2 \chi = -\frac{1}{2} J(\overline{\partial}_{A_{0, 1}} \psi)$ and zero on other fields.
